\chapter{System Description}\label{chap:systemDescribtion}

\input{chapters/sensors.tex}

\section{Actuators}
 
\subsection{Reaction Wheels}

One method of controlling a spacecraft's attitude is by using either reaction or momentum wheels attached to the spacecraft's body. By controlling the wheel's angular velocity using a motor, the amount of angular momentum stored in the wheel can be controlled. If there are no external forces involved, the sum of angular momentum in the system made up by the spacecraft's body and the reaction wheels is constant. This means that by increasing the angular velocity of the wheels, the satellite body's angular momentum can be reduced. This angular momentum transfer can be used to control the attitude of the satellite. If the goal is to change the angular momentum of the whole satellite, actuators that have external interaction should be used, such as magnetorquers or solar sails.

The difference between momentum and reaction wheels is that the nominal angular velocity of momentum wheels is high in order to store angular momentum, and in the case of reaction wheels, low. Many momentum wheels still turn at an angular velocity larger than zero in order to avoid static friction in the bearings. Reaction wheels usually make up only a small fraction of a satellite's weight. They rely on being able to run at high speeds, making their angular momentum significant. The small weight ratio makes precise controlling easier.


%One design consideration for reaction wheels is maximizing moment of inertia for unit weight. This is done by distributing most of the material near the outskirts of the wheel. There is a trade-off between having most of the mass at the outskirts and durability at high angular velocities. 


Reaction wheels have an angular velocity limitation. This means that if a reaction wheel reaches its maximum angular velocity, it can no longer generate a torque on the satellite's body in one direction. In this scenario the system's controllability decreases, thus it should be avoided. An angular momentum unloading strategy should be designed to avoid it. Instead of returning the angular momentum to the satellite's body, unloading the angular momentum through other methods is preferred. Magnetorquers can be used for such purposes.

Moving parts are usually prone to failures. Reaction wheels are expected to run at high angular velocities, which wears down the lubrication and the bearings. Reaction wheels equipped with active magnetic bearings are in development \cite{MagneticReactWheel}. These can eliminate friction from the system and by controlling the bearing, can even reduce micro-vibrations, increasing the durability of the system. AAUSAT-II itself however uses mechanical wheel bearings.

\subsection{Reaction Wheel Configuration}

angular acceleration demand \cite{reactionWheelConfigThesis} 

gps orientation, Earth station

Tetrahedron configuration can output twice as much force along an axis as one wheel can produce along its own axis.

\subsubsection{Transformation Between Body \& Reaction Wheel Space}

The main attitude controller sends torque demands to the actuators. The torque demand distributed to the reaction wheels have to be converted to torques parallel to reaction wheel axes, in order for the motor controllers to function. Transformation from reaction wheel space to body frame is quite intuitive. Knowing the orientation of each motor axis and the corresponding motor torque 
, the torque in body frame can be derived according to equation \ref{eq:motorTrans1} - \ref{transmatrix}. The matrix for tetrahedron configuration is given by \cite{reactionWheelConfigThesis}.

\begin{equation}
\label{eq:motorTrans1}
\vec{N_{rw}} = \underline{A}_{DC} \vec{N_{DC}} = \begin{bmatrix}
\vec{Axis^{DC}_{1}}       & \vec{Axis^{DC}_{2}}   & \vec{Axis^{DC}_{3}}   & \vec{Axis^{DC}_{4}} 
\end{bmatrix} \vec{N_{DC}}
\end{equation}

\begin{equation}
\underline{A}_{DC} \vec{N_{DC}}  = 
\begin{bmatrix}
\cos(19.47)       & -\cos(19.47) \cos(60)  &  -\cos(19.47) \cos(60)  & 0 \\
0       & \cos(19.47) \cos(30)  &  -\cos(19.47) \cos(30)  & 0 \\
-\sin(19.47)       & -\sin(19.47)   &  -\sin(19.47)   & 1
\end{bmatrix} \vec{N_{DC}}
\label{transmatrix}
\end{equation}

where $\vec{N_{rw}}$ is the reaction wheel torque in body frame, $\vec{N_{DC}}$ is the vector containing the reaction wheel DC motor torques parallel to their axes, $\vec{Axis^{DC}_{i}}$ are the reaction wheel motor orientation in body frame, $\underline{A}_{DC}$ is the transformation matrix between axis oriented reaction wheel torque and torques in 3 dimensional body frame.


\nomenclature[S]{$\vec{N_{rw}}$}{Reaction wheel torque in body frame }
\nomenclature[S]{$\vec{N_{DC}}$}{$4\times1$ vector containing the reaction wheel motor motor torques parallel to their axes }
\nomenclature[S]{$\underline{A}_{DC}$}{Transformation matrix between axis oriented reaction wheel torque and torques in 3 dimensional body frame }

Since $\underline{A}_{DC} $ is a $ 4 \times 3 $ matrix, a pseudo inverse has to be used when reordering the equation, as presented in equation \ref{eq:motorTrans}. 

\begin{equation}
\label{eq:motorTrans}
\vec{N_{DC}} =  \underline{A}_{DC} ^\dagger \vec{N_{rw}}   =  \underline{A}_{DC}^T  (\underline{A}_{DC} \underline{A}_{DC} ^T)^{-1} \vec{N_{DC}}
\end{equation}


%\begin{equation}
%h_{rot} = A\left[ h_1, h_2, h_3, h_4 \right]^T
%\end{equation}

In case there's a demand to adjust the torque distribution between the wheels, an extra vector can be included, as shown in equation \ref{eq:TorqueDistrib}
\cite[equation 18.41-42]{SADC}. If k is set to 0, the norm of wheel torques are minimized.

\begin{equation}
\label{eq:TorqueDistrib}
 \vec{N_{DC}} = \underline{A}^\dagger_{DC} \vec{N_{rw}}  + k\left[1,-1,-1,1\right]^T
\end{equation}


\subsubsection{Reconfiguration}

Fault isolation for the redundant reaction wheel configuration can be done by detecting which is the reaction wheel where the fault occurred and shutting it off and redistributing the torques to the rest of the reaction wheels. This reconfiguration can be represented by swapping the corresponding faulty columns to zero vectors. For example, if a fault occurs in the 3rd reaction wheel, the transformation matrix becomes $\underline{A}_{DC,f3}$, as presented in equation \ref{eq:ReactFault}.

\begin{equation}
\label{eq:ReactFault}
\underline{A}_{DC,f3} = \begin{bmatrix}
\vec{Axis^{DC}_{1}}       & \vec{Axis^{DC}_{2}}   & \vec{0}   & \vec{Axis^{DC}_{4}} 
\end{bmatrix} 
\end{equation}

\nomenclature[S]{$\underline{A}_{DC,fi}$}{Transformation matrix between axis oriented reaction wheel torque and torques in 3 dimensional body frame in case of faulty $i$th reaction wheel}

The pseudo inverse is calculated in the same manner as presented in equation \ref{eq:motorTrans}, as shown in equation \ref{eq:motorTransFault}. 

\begin{equation}
\label{eq:motorTransFault}
\underline{A}_{DC,f3}^\dagger   = \underline{A}_{DC,f3}^T  (\underline{A}_{DC,f3} \underline{A}_{DC,f3}^T)^{-1}
\end{equation}


\input{chapters/motorModAndCont.tex}
\input{chapters/motor/torqueControl.tex}
\input{chapters/magnetorquer.tex}

